\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students

### 2023-09-04 phd-cs-us.tex
Updates from Overleaf

\begin{wrapfigure}{r}{0.52\linewidth}
\vspace{-0.2in}
    \begin{center}
      \includegraphics[width=1\linewidth]{c2.png}
    \end{center}
    \vspace{-0.2in}
  \end{wrapfigure}
While you might not have control over LORs \hyperref[sec:your-school]{where your go to school}, you do over your
statement! So write it well because we take it seriously.
In your statement, you have the opportunity to make  make your application stand out and unique, which can make you \emph{fit} the CS program you're applying to, even if you don't have very strong research experience.
A well-written LOR also shows that you can communicate, which is very important in research, and that you can effectively teach and communicate with students, which is important for TA funding (see \S\ref{sec:funding}).
%is important because if you need (GTA) funding, it will provide evidence
%that you can teach and communicate with students.

@@

\begin{wrapfigure}{r}{0.48\textwidth}
\vspace{-0.2in}
      \begin{center}
        \includegraphics[width=1\linewidth]{c8.png}
      \end{center}
      \vspace{-0.2in}
    \end{wrapfigure}
The short answer is that tenured-track faculty such as assistant professors are more likely to be young and active in research (they have to, in order to get tenure). Thus, they will likely have more time to work with you and push you to do research and publish. However, they may not have as much experience in managing students and may not have as much funding (yet).

@@

\begin{wrapfigure}{r}{0.35\textwidth}
\vspace{-0.2in}
\begin{center}
\includegraphics[width=1\linewidth]{c4a.png}
\end{center}
\vspace{-0.3in}
\end{wrapfigure}
    Typically, 5--7 years for PhD in CS in the US.  This can be longer than CS PhD at universities in other countries, which might require MS first (recall that US PhD programs do not require MS and you can get MS along the way to PhD). Within these 5--7 years, CS PhD students in the US also often take a ``leave of absence'' for 1--2 semesters to do internship at companies and research labs.

@@

\begin{wrapfigure}{l}{0.5\linewidth}
\vspace{-0.3in}
      \begin{center}
        \includegraphics[width=1\linewidth]{c5.png}
      \end{center}
      \vspace{-0.5in}
    \end{wrapfigure}
If you don't know the professor (e.g., first email contact), then use \textbf{Prof. Lastname} or \textbf{Dr. Lastname}. I've seen many international students write \textbf{Prof.} or \textbf{Dr.} \textbf{Firstname Lastname}.  Writing like that makes it like you copy and paste names, so no need to do so,  just Prof. or Dr. Lastname.

If you don't know the prof., do not use Mr. or Mrs., or Firstname. To me it seems a bit disrespectful. As you know that prof. better and depends on their preference, you may call them by their Firstname.

>>>>

    \begin{center}
      \includegraphics[scale=0.5]{c2.png}
    \end{center}

While you might not have control over LORs \hyperref[sec:your-school]{where your go to school}, you do over your
statement! So write it well because we take it seriously.
In your statement, you have the opportunity to make  make your application stand out and unique, which can make you \emph{fit} the CS program you're applying to, even if you don't have very strong research experience.
A well-written LOR also shows that you can communicate, which is very important in research, and that you can effectively teach and communicate with students, which is important for TA funding (see \S\ref{sec:funding}).
%is important because if you need (GTA) funding, it will provide evidence
%that you can teach and communicate with students.

@@

      \begin{center}
        \includegraphics[scale=0.3]{c8.png}
      \end{center}

The short answer is that tenured-track faculty such as assistant professors are more likely to be young and active in research (they have to, in order to get tenure). Thus, they will likely have more time to work with you and push you to do research and publish. However, they may not have as much experience in managing students and may not have as much funding (yet).

@@

\begin{center}
\includegraphics[scale=0.3]{c4a.png}
\end{center}

    Typically, it takes 5--7 years for CS PhD in the US.  This can be longer than CS PhDs at universities in other countries, which might require MS first (recall that US PhD programs do not require MS and you can get MS along the way to PhD). Within these 5--7 years, CS PhD students often take a ``leave of absence'' for 1--2 semesters to do internship at companies and research labs.

@@

      \begin{center}
        \includegraphics[scale=0.5]{c5.png}
      \end{center}

If you don't know the professor (e.g., first email contact), then use \textbf{Prof. Lastname} or \textbf{Dr. Lastname}. I've seen many international students write \textbf{Prof.} or \textbf{Dr.} \textbf{Firstname Lastname}.  Writing like that makes it like you copy and paste names, so no need to do so,  just Prof. or Dr. Lastname.
Moreover, if you don't know the prof., do not use Mr. or Mrs., or Firstname. To me it seems a bit disrespectful. As you know that prof. better and depends on their preference, you may call them by their Firstname.
